Survivable Set Connectivity

### 2015-05-10 draft.tex
fixed a typo
changed margins,rewrote LP formulation sections, fixed typos

\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{clrscode4e}

@@

Unfortunately, solving exact Survivable Set Connectivity is $\mathsf{NP}$-hard [CITATION]. Therefore, the focus of this paper is on an approximate solution to a relaxation of this problem. Instead of requiring at least $k$ edge-disjoint paths between each pair, we require that each pair have at least $\Omega(\frac{k}{\log n})$ edge-disjoint paths. With this relaxation, it is possible to find a subgraph with cost $O(polylog(n)$ times the optimum.

@@

\section{Linear Programming Formulation}

We can formulate a cut-based integer linear program for SSC. For each edge, we have the variable $x_e$ defined as
\begin{align}
 x_e &= \left\{ \begin{array}{cc} 1 & e \in H \\
                                  0 & \text{ otherwise. } \end{array} \right.
\end{align}
$H$ will be the subgraph consisting of edges $e$ where $x_e = 1$. \\ \\
SSC-LP:
\begin{align}
\min & \sum c(x) x_e  \\
\text{ s.t } & \sum_{e \in \delta(S)} x_e \geq k, \text{ where } S_i \subset S, T_i \subset V - S, \delta(S) \text{ is the edges of the $S$ cut }
\end{align}
This cut-based integer linear program finds exactly $H$. To see why the constraints ensure that each $(S_i, T_i)$ pair has at least $k$ edge disjoint paths, we can look at the cuts corresponding to $S_i$ and $T_i$. First, we let $S = S_i$, then there are $k$ outgoing edges. We can choose to include one more node to $S$, following a particular outgoing edge of the cut in $H$. We can continue doing this until we reach $T_i$. This will trace out a path between $S_i$ and $T_i$. If we do this for each edge, and then we do this for each $(S_i, T_i)$ pair, we can confirm that there are in fact $k$ edge-disjoint paths between each $(S_i, T_i)$ pair.

There is one caveat that has not been addressed. We have exponentially many constraints! Since there can be exponentially many set $S$ with $S_i \subset S$ and $T_i \subset V - S$. We solve this with a similar idea to semi-definite programming, by giving a separation oracle which runs in polynomial time.

The separation oracle will just compute the minimum $S_i, T_i$ cut in the graph. What we can do is contract $S_i$ and $T_i$ to single edges, and then compute the min-cut in the remaining graph. If there is a min-cut of size less than $k$, then that cut will correspond to a violating contraint. If the min-cut has size at least $k$, then all cuts have size at least $k$, so we have satisfied the constraints.

The linear programming relaxation to the above program will be the first step of the algorithm. The remaining work will be rounding the fractional solution to an integral solution and satisfy the constraints.

@@

Figure~\ref{fig:racketree} gives an example of the flow correspondnece between a graph and it's associated R\"{a}cke's tree. Each red vertex of the tree is mapped to another red vertex on the graph, and the edge between them corresponds to a path between the red vertices. This gives us a simple way to map flows from Racke trees to the graph and vice-versa.

>>>>

\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{clrscode4e}
\usepackage{geometry}
 \geometry{
 a4paper,
 total={210mm,297mm},
 left=20mm,
 right=20mm,
 top=20mm,
 bottom=20mm,
 }

@@

Unfortunately, solving exact Survivable Set Connectivity is $\mathsf{NP}$-hard [CITATION]. Therefore, the focus of this paper is on an approximate solution to a relaxation of this problem. Instead of requiring at least $k$ edge-disjoint paths between each pair, we require that each pair have at least $\Omega(\frac{k}{\log n})$ edge-disjoint paths. With this relaxation, it is possible to find a subgraph with cost $O(polylog(n))$ times the optimum.

@@

\section{An Integer Linear Program}

In this section, we give an integer linear program that exactly solves SSC. Recall that the goal is to output a subgraph $H$ of $G$ such that each $(S_i,T_i)$ pair has at least $k$ edge disjoint paths. Naturally, we create an indicator variable $x_e$ for each edge based on whether or not it is included in $H$. 
\begin{align}
 x_e &= \left\{ \begin{array}{cc} 1 & e \in H \\
                                  0 & \text{ otherwise. } \end{array} \right.
\end{align}
Thus, our output $H$ will be the subgraph consisting of edges $e$ where $x_e = 1$. \\ \\

We claim that the following ILP captures SSC exactly. 
SSC-LP:
\begin{align}
\min & \sum c(x) x_e  \\
\text{ s.t } & \sum_{e \in \delta(S)} x_e \geq k, \text{for each }S\text{ where } S_i \subset S,T_i \subset V - S, \\ & \hspace{1in}\delta(S) \text{ is the edges of the $S$ cut } \\
& x_e \in [0,1] \text{ for all }e \in E
\end{align}

The objective function $\sum c(x) x_e$ simply minimizes the cost of all edges included in $H$. The constraint ensures that for all pairs $(S_i,T_i)$, any cut where $S_i$ is on one side of the cut and $T_i$ is on the other side has at least $k$ edges crossing the cut. This property holds if and only if there are $k$ edge disjoint paths from $S_i$ to $T_i$. We omit the proof of this statement, but it can be found in [CITATION].

%
%
% 
%This cut-based integer linear program finds exactly $H$. To see why the constraints ensure that each $(S_i, T_i)$ pair has at least $k$ edge disjoint paths, we can look at the cuts corresponding to $S_i$ and $T_i$. First, we let $S = S_i$, then there are $k$ outgoing edges. We can choose to include one more node to $S$, following a particular outgoing edge of the cut in $H$. We can continue doing this until we reach $T_i$. This will trace out a path between $S_i$ and $T_i$. If we do this for each edge, and then we do this for each $(S_i, T_i)$ pair, we can confirm that there are in fact $k$ edge-disjoint paths between each $(S_i, T_i)$ pair.

Of course, since this is an integer linear program, we must relax it to fractional solutions in order to solve it. Thus, we relax the constraint of $x_e \in [0,1]$ to $0 \leq x_e \leq 1$. However, there is still a slight issue; there can be exponentially many constraints. This is because there are exponentially many choices of $S$ for each $(S_i,T_i)$ pair. To get around this issue, we note that the ellipsoid algorithm can handle linear programs with arbitrarily many constraints, as long as it is given a separation oracle. Luckily, we can give such an oracle.

The separation oracle just computes the minimum $S_i, T_i$ cut in the graph. What we can do is contract $S_i$ and $T_i$ to single vertices, and then compute the min-cut in the remaining graph. If there is a min-cut of size less than $k$, then that cut will correspond to a violating contraint. If the min-cut has size at least $k$, then all cuts have size at least $k$, so we have satisfied the constraints.

@@

Figure~\ref{fig:racketree} gives an example of the flow correspondence between a graph and it's associated R\"{a}cke's tree. Each red vertex of the tree is mapped to another red vertex on the graph, and the edge between them corresponds to a path between the red vertices. This gives us a simple way to map flows from Racke trees to the graph and vice-versa.
